Analytic Occultation Light Curves in Reflected Light

### 2020-05-04 tex/ms.tex
more figs

The piecewise nature of the illumination function at the day/night terminator
makes the problem of computing the visible flux particularly difficult; most
studies to date have tackled the problem numerically, by discretizing the surface
and computing the relevant integrals by summing over the visible
pixels \xxx{(cite)}. Recently, \citep{Haggard2018} developed an analytic
framework for computing light curves of unocculted bodies illuminated
by a point source. In this paper, we re-derive their solution under the
\starry framework and extend it for the first time to the case where
the body is occulted by another spherical body, which may or may not be the
illumination source.

@@

Figure~\ref{fig:earthmoon} shows a sample application of the algorithm
developed in this paper. The figure shows two mock occultation light curves
of the cloudless Earth as the Moon is seen to transit its disk, both computed
using \starry from an $l=25$ expansion of the map of the Earth.
The top panel shows an occultation in emitted light and is a reproduction of
Figure~7 in \citet{Luger2019}. The bottom panel shows a light curve for the
same occultation geometry, but seen instead in reflected light, with the
Sun to the top left and slightly out of the page.
The black curves correspond to the analytical solution, and the orange dots
to the brute force numerical solution, obtained by discretizing the disk
on a grid of ${\sim}10^6$ points. The solutions agree to within the
numerical precision of the brute force solution (about 100 ppm in this
case).

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/earthmoon_emitted.pdf}
        \includegraphics[width=\linewidth]{figures/earthmoon.pdf}
        \oscaption{earthmoon}{%
            Mock light curves of the Moon occulting a rotating,
            cloudless Earth expanded to spherical harmonic degree $l = 25$.
            Black curves show the analytic solution; orange dots correspond
            to brute force numerical integration on a grid of
            ${\sim}10^6$ points.
            The top panel shows the light curve in emitted light and is
            equivalent to Figure~7 in \citet{Luger2019}.
            The bottom panel (this work) shows the same light curve in
            reflected light during northern summer.
            \label{fig:earthmoon}
        }
    \end{centering}
\end{figure}

@@

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/oren_nayar.pdf}
        \oscaption{oren_nayar}{%
            Intensity measured from a sphere at varying illumination
            phase under the \citet{OrenNayar1994} scattering model.
            The top panel shows spheres rendered with different surface
            roughness coefficients ranging from $\sigma = 0^\circ$
            (the Lambertian case) to $\sigma = 45^\circ$. The bottom
            panel shows the corresponding phase curves for a sphere
            of unit spherical albedo illuminated by a point source
            at $r_s = 1$, computed
            analytically from a degree \STARRYQUADPOINTS expansion
            of the scattering law. Dots
            correspond to the intensity computed numerically directly
            from Equation~(30) in \citet{OrenNayar1994}.
            \label{fig:oren_nayar}
        }
    \end{centering}
\end{figure}
%

@@

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/io_europa.pdf}
        \oscaption{io_europa}{%
            Visible-light occultation of Io by Europa observed
            on 04 Dec 2009 by the PHEMU09 campaign \citep{Arlot2014}.
            The blue line is the \starry model, based of an
            $l=15$ spherical harmonic fit to the
            Galileio global color mosaic of Io \citep{Becker2005},
            an $l=\STARRYQUADPOINTS$ expansion of the
            \citep{OrenNayar1994} scattering law, and orbital
            information from the JPL Horizons \xxx{(cite)} database.
            See text for details.
            \label{fig:io_europa}
        }
    \end{centering}
\end{figure}
%

>>>>

The piecewise nature of the illumination function at the day/night terminator
makes the problem of computing the visible flux particularly difficult; most
studies to date have tackled the problem numerically, by discretizing the surface
and computing the relevant integrals by summing over the visible
pixels \xxx{(cite)}. Recently, \citet{Haggard2018} developed an analytic
framework for computing light curves of unocculted bodies illuminated
by a point source. In this paper, we re-derive their solution under the
\starry framework and extend it for the first time to the case where
the body is occulted by another spherical body, which may or may not be the
illumination source.

@@

Figure~\ref{fig:earthphase} shows...

\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/earthphase.pdf}
        \oscaption{earthphase}{%
            Mock reflected light  phase curve of the cloudless Earth expanded
            to spherical harmonic degree $l = 25$. The main plot shows the
            phase curve over the course of one year.
            \label{fig:earthphase}
        }
    \end{centering}
\end{figure}

Figure~\ref{fig:earthmoon} shows a sample application of the algorithm
developed in this paper. The figure shows two mock occultation light curves
of the cloudless Earth as the Moon is seen to transit its disk, both computed
using \starry from an $l=25$ expansion of the map of the Earth.
The top panel shows an occultation in emitted light and is a reproduction of
Figure~7 in \citet{Luger2019}. The bottom panel shows a light curve for the
same occultation geometry, but seen instead in reflected light, with the
Sun to the top left and slightly out of the page.
The black curves correspond to the analytical solution, and the orange dots
to the brute force numerical solution, obtained by discretizing the disk
on a grid of ${\sim}10^6$ points. The solutions agree to within the
numerical precision of the brute force solution (about 100 ppm of the
planetary flux in this case).

\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/earthmoon_emitted.pdf}
        \includegraphics[width=\linewidth]{figures/earthmoon.pdf}
        \oscaption{earthmoon}{%
            Mock light curves of the Moon occulting a rotating,
            cloudless Earth expanded to spherical harmonic degree $l = 25$.
            Black curves show the analytic solution; orange dots correspond
            to brute force numerical integration on a grid of
            ${\sim}10^6$ points.
            The top panel shows the light curve in emitted light and is
            the same as in Figure~7 in \citet{Luger2019}.
            The bottom panel (this work) shows the same light curve in
            reflected light during northern summer.
            \label{fig:earthmoon}
        }
    \end{centering}
\end{figure}

Figure~\ref{fig:earthsun} shows

\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/earthsun_emitted.pdf}
        \includegraphics[width=\linewidth]{figures/earthsun.pdf}
        \includegraphics[width=\linewidth]{figures/earthsun_diff.pdf}
        \oscaption{earthsun}{%
            Mock secondary eclipse light curves of the
            cloudless Earth expanded to spherical harmonic degree $l = 25$.
            Black curves show the analytic solution; orange dots correspond
            to brute force numerical integration on a grid of
            ${\sim}10^6$ points.
            The top panel shows the light curve in emitted light and is
            similar to Figure~13 in \citet{Luger2019}.
            The middle panel (this work) shows the same light curve in
            reflected light.
            The bottom panel shows the difference between the
            normalized reflected and normalized emitted light curves.
            \label{fig:earthsun}
        }
    \end{centering}
\end{figure}

% DEBUG
\pagebreak

@@

\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/oren_nayar.pdf}
        \oscaption{oren_nayar}{%
            Intensity measured from a sphere at varying illumination
            phase under the \citet{OrenNayar1994} scattering model.
            The top panel shows spheres rendered with different surface
            roughness coefficients ranging from $\sigma = 0^\circ$
            (the Lambertian case) to $\sigma = 45^\circ$. The bottom
            panel shows the corresponding phase curves for a sphere
            of unit spherical albedo illuminated by a point source
            at $r_s = 1$, computed
            analytically from a degree \STARRYQUADPOINTS expansion
            of the scattering law. Dots
            correspond to the intensity computed numerically directly
            from Equation~(30) in \citet{OrenNayar1994}.
            \label{fig:oren_nayar}
        }
    \end{centering}
\end{figure}
%

@@

\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/io_europa.pdf}
        \oscaption{io_europa}{%
            Visible-light occultation of Io by Europa observed
            on 04 Dec 2009 by the PHEMU09 campaign \citep{Arlot2014}.
            The blue line is the \starry model, based of an
            $l=15$ spherical harmonic fit to the
            Galileio global color mosaic of Io \citep{Becker2005},
            an $l=\STARRYQUADPOINTS$ expansion of the
            \citet{OrenNayar1994} scattering law, and orbital
            information from the JPL Horizons \xxx{(cite)} database.
            See text for details.
            \label{fig:io_europa}
        }
    \end{centering}
\end{figure}
%

\pagebreak
